### 2023-03-13 manuscript.Rmd
Re-factor file structure, rating functions

bibliography      : "manuscript_files/references.bib"
csl               : "manuscript_files/citation_style.csl"

@@

output:
  papaja::apa6_pdf:
    latex_engine: xelatex
    pandoc_args: ["--lua-filter=manuscript_files/color_text.lua"]

@@

```{r, setup, include=FALSE}
# Load R packages
library(buildmer)
library(emmeans)
library(here)
library(knitr)
library(lmerTest)
library(MASS)
library(scales)
library(papaja)
library(eegUtils)
library(cowplot)
library(parallel)
library(reticulate)
library(tidyverse)

# Set global options
options(readr.show_col_types = FALSE)
opts_chunk$set(
  fig.pos = "tp",
  fig.width = 12,
  message = FALSE,
  out.width = "100%",
  warning = FALSE
)

# Specify directory paths
data_dir <- here("data")
rating_dir <- here(data_dir, "ratings")
files_dir <- here("manuscript_files")
output_dir <- here("output")
report_dir <- here(output_dir, "qc_reports")

# Load custom helper functions for creating figures and tables
source(here(files_dir, "helper_functions.R"))

# Re-run steps that take a long time to compute?
run <- list(
  rating_semantic_analysis = FALSE,
  eeg_processing = FALSE,
  mixed_models = FALSE,
  figures = FALSE
)

# Write R packages to bibliography
r_refs(here(files_dir, "r-references.bib"), append = FALSE)
```

@@

```{r, ratings}
# Read table of object stimuli + keywords for the main experiment
keywords <- read_csv(
  here("materials", "keywords.csv"),
  col_types = cols(
    familiarity = col_factor(levels = c("familiar", "unfamiliar")),
    item_id = col_factor()
  )
) %>%
  mutate(
    match = str_c(match_noun, ", ", match_verb),
    match_en = str_c("{[", match_noun_en, ", ", match_verb_en, "]}"),
    nonmatch = str_c(nonmatch_noun, ", ", nonmatch_verb),
    nonmatch_en = str_c("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
  )

# (Re-)do latent semantic analysis of online rating study data
rating_file <- here(output_dir, "rating.csv")
if (run$rating_semantic_analysis) {
  # Load pre-trained German word2vec embedding
  word2vec <- load_word2vec(rating_dir)

  # Read online rating study data
  rating_raw <- read_csv(
    here(data_dir, "ratings", "rating_data.csv"),
    col_types = cols(), locale = locale(encoding = "latin1")
  )
  rating_substantives <- select(rating_raw, S001_01:S242_01)
  rating_verbs <- select(rating_raw, V001_01:V242_01)

  # Prepare a copy of the keywords to add to the rating study data
  rating_n <- nrow(rating_raw)
  keywords_for_rating <- keywords %>%
    arrange(familiarity, filename) %>%
    select(item_id, familiarity, filename, match, nonmatch) %>%
    replicate(rating_n, ., simplify = FALSE) %>%
    bind_rows()

  # Compute cosine similarities between rating study responses and keywords
  rating <-
    map2_dfc(rating_substantives, rating_verbs, str_c, sep = ", ") %>%
    mutate(participant_id = rating_raw$CASE) %>%
    pivot_longer(
      -participant_id,
      names_to = "question_id", values_to = "response"
    ) %>%
    bind_cols(keywords_for_rating, .) %>%
    pivot_longer(
      c(match, nonmatch),
      names_to = "condition", values_to = "keywords"
    ) %>%
    mutate(
      condition = ifelse(condition == "match", "matching", "non-matching"),
      across(c(keywords, response), str_to_lower),
      keywords = str_replace_all(
        keywords, c(
          aufstemmen = "aufbrechen",
          tierkäfig = "käfig",
          wegkehren = "kehren",
          verühren = "rühren",
          schraubenschlüssel = "werkzeug",
          verquirlen = "rühren",
          tackern = "tacker",
          sprengstoffexplosion = "explosion",
          tankfüllstand = "füllstand",
          tonpott = "tongefäß",
          eierkarton = "eier verpackung",
          musikgerät = "musikinstrument",
          türgelenk = "scharnier",
          telegrafieren = "telegraf",
          sternenbilder = "sternbild",
          aufspulen = "aufwickeln",
          häckseln = "zerkleinern",
          `mikroskop-proben` = "mikroskop proben",
          streckenmaß = "maß",
          windgeschwindigkeit = "windstärke",
          nussöl = "nuss öl",
          entkörnen = "entkernen",
          katzenklo = "katze klo",
          kutschrad = "kutsche rad"
        )
      ),
      response = str_replace_all(
        response, c(
          aufhebeln = "aufbrechen",
          föhnen = "föhn",
          kasette = "kassette",
          aufkehren = "kehren",
          tackern = "tacker",
          sprayapparat = "spray apparat",
          anästhesieren = "betäuben",
          reaktionsspiel = "reaktion spiel",
          mulchgerät = "mulch gerät",
          makierung = "markierung",
          wissenschaftlich = "wissenschaft",
          spannwerkzeug = "werkzeug",
          wärmestab = "wärme stab",
          ampfel = "ampel",
          scheere = "schere",
          pflägen = "pflügen",
          knetten = "kneten",
          pfandkuchen = "pfannkuchen",
          anmacher = "anmachen",
          injezieren = "injizieren",
          telfon = "telefon",
          beschrifter = "beschriften",
          aufbewaren = "aufbewahren",
          spähne = "späne",
          separator = "trennen",
          stämpfer = "stampfen",
          fliente = "flinte",
          tromphete = "trompete",
          makieren = "markieren",
          stöbseln = "stöpsel",
          hiernwellen = "gehirnwellen",
          kartofeln = "kartoffeln",
          vaccum = "vakuum",
          saubermachen = "putzen",
          ankeln = "anker",
          schuessel = "schüssel",
          `zangen\\\\` = "zange",
          kleiderbuegel = "kleiderbügel",
          buerste = "bürste",
          buersten = "bürsten",
          druecken = "drücken",
          obstscheider = "obst schneiden",
          àumachen = "ausmachen",
          bieroeffner = "flaschenöffner",
          oeffnen = "öffnen",
          giesskanne = "gießkanne",
          gluehbirne = "glühbirne",
          schettem = "manschetten",
          kurzhantel = "kurzhanteln",
          tierekiste = "tiere kiste",
          kaffekocher = "kaffeemaschine",
          kinderwaagen = "kinderwagen",
          klobürste = "toilette bürste",
          orangenpresser = "orangen presse",
          foodmixer = "essen mixer",
          schuessel = "schüssel",
          naehen = "nähen",
          teigwalze = "nudelholz",
          pffefern = "pfeffer",
          maehen = "mähen",
          gesichtsbürste = "gesicht bürste",
          regenchirm = "regenschirm",
          kaesegratin = "käse gratin",
          slotsmaschine = "slot maschine",
          piggybank = "sparschwein",
          stampen = "kleben",
          arztwekzeug = "arzt werkzeug",
          gradskala = "grad skala",
          trichten = "trichter",
          spulsmaschine = "spülmaschine",
          zahnbrueste = "zahnbürste",
          bruesten = "bürsten",
          foltermaschine = "folter maschine",
          bieröffner = "flaschenöffner",
          oeffnen = "öffnen",
          pizzacutter = "pizza schneider",
          kerzestande = "kerzenständer",
          naehen = "nähen",
          geruest = "gerüst",
          nagelschneider = "nagel schere",
          burste = "bürste",
          bursten = "bürsten",
          loefel = "löffel",
          hamsterspielzeug = "hamster spielzeug",
          breadboard = "schneide brett",
          druceken = "drücken",
          nussknacnker = "nussknacker",
          ueberwachen = "überwachen",
          trainingsmaschine = "training maschine",
          padeln = "paddeln",
          schäumer = "aufschäumen",
          aufhanger = "aufhänger",
          hangt = "hängen",
          `eier-guillotine` = "eier messer",
          ruhrgerat = "rührgerät",
          katzentrager = "katzen träger",
          hinzufugen = "hinzufügen",
          kuchenform = "backform",
          nagelfeile = "nagel feile",
          fondues = "fondue",
          zuhoren = "zuhören",
          rasenmaher = "rasenmäher",
          geschlitzter = "schlitz",
          breifmarke = "briefmarke",
          bimmeln = "läuten",
          rasma = "",
          kassete = "kassette",
          nudelmaschine = "nudel maschine",
          ruhrer = "rührer",
          feuerloscher = "feuerlöscher",
          entfernungsmesser = "entfernung messer",
          heißluftpistole = "heißluft pistole",
          schuhlöffel = "schuhe anziehen",
          uben = "üben",
          naturlich = "natürlich",
          schißen = "schießen",
          rührgerät = "mixer",
          aufkehren = "kehren",
          rausziehen = "herausziehen",
          `mini-meißel` = "mini meißel",
          kaffeemischer = "kaffee mischer",
          nachttischlampe = "nachttisch lampe",
          arbeitsschlüssel = "arbeit schlüssel",
          `boom-box` = "lautsprecher",
          feststampfen = "fest stampfen",
          `casino-maschine` = "casino maschine",
          `herzfrequenz-test` = "herzfrequenz test",
          zaichnen = "zeichnen",
          schneidin = "schneiden",
          vergleichsmaschine = "vergleich maschine",
          rosenabzeichen = "rosen abzeichen",
          `dummy-stecker` = "dummy stecker",
          `post-punk-sanduhr` = "post punk sanduhr",
          schneidemaschine = "schneiden maschine",
          fusszeile = "fußzeile",
          gartenlampe = "garten lampe",
          trenneimer = "trennen eimer",
          fußabstreifer = "fußmatte",
          wichten = "gewicht",
          perlenständer = "perlen ständer",
          briefmarker = "briefmarke",
          `elektronische-schaltung` = "elektronische schaltung",
          fläschchenheizung = "flächen heizung",
          elektrodrucker = "elektro drucker",
          metalllinse = "metall linse",
          kugelheizung = "kugel heizung",
          abschrauber = "abschrauben",
          `mini-korb` = "mini korb",
          elektronenrechner = "elektronen rechner",
          spießfaum = "spieß",
          tierträger = "tier träger",
          rührgerät = "rührgerät",
          kuchenform = "backform",
          friteuse = "fritteuse",
          `ein-` = "ein",
          greigfen = "greifen",
          zerknittern = "falten bekommen",
          salatzange = "salat zange",
          wwrm = "wurm",
          duschwasser = "dusche wasser",
          verbreitene = "verbreiten",
          aufpieksen = "anstechen",
          restriktieren = "einschränken",
          rückgeld = "wechselgeld",
          aufkehren = "zusammenkehren",
          bratgut = "grillgut",
          bepinseln = "bestreichen",
          verquirlen = "vermischen",
          temparatur = "temperatur",
          aufspulen = "aufwickeln",
          elekronik = "elektronik",
          festnieten = "fest nieten",
          festspannen = "fest spannen",
          hebelkräfte = "hebelkraft",
          meiseln = "meißeln",
          betäüben = "betäuben",
          verschraüben = "verschrauben",
          schraüben = "schrauben",
          seperator = "trennen",
          schraübendreher = "schraubendreher",
          gegewicht = "gewicht"
        )
      ),
      cosine = compute_cosine(keywords, response, word2vec)
    )

  # Save to file
  write_csv(rating, rating_file)
}

# # Test if all keywords and responses are in the embedding
# for (keywords in c(unique(rating$keywords), unique(rating$response))) {
#   if (!is.na(keywords)) {
#     for (word in (str_split(keywords, pattern = " |, ")[[1]])) {
#       if (!(word %in% rownames(word2vec))) {
#         cat(paste0(word, ' = "",\n'))
#       }
#     }
#   }
# }

# Read the rating study results incl. cosine similarities
rating <- read_csv(
  rating_file,
  col_types = cols(item_id = col_factor(), participant_id = col_factor())
) %>%
  filter(!is.na(cosine)) %>%
  mutate(
    fam_condition = paste(familiarity, condition) %>%
      factor(
        levels = c(
          "familiar matching", "unfamiliar matching", "unfamiliar non-matching"
        ),
        labels = c("familiar", "matching", "nonmatching")
      )
  )

# Compare cosine similarities between object conditions
contrasts(rating$fam_condition) <- contr.sdif(3)
model_rating <- lmer(
  cosine ~ fam_condition +
    (fam_condition | participant_id) +
    (1 | item_id),
  data = rating,
  control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6))
)

# Compute condition means and pairwise contrasts
emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
emm_rating <- emmeans(
  model_rating,
  specs = consec ~ fam_condition,
  rev = TRUE,
  adjust = "bonferroni"
)
rating_means <- as.data.frame(emm_rating$emmeans)
rating_contrasts <- as.data.frame(emm_rating$contrasts) %>%
  rename(t_value = `t.ratio`, p_value = `p.value`)

# Compute each item's average cosine distance across participants
cosines <- rating %>%
  group_by(item_id) %>%
  summarize(cosine = mean(cosine)) %>%
  mutate(cosine = scale(cosine))

# rating_pairwise <- rating$participant_id %>%
#   unique() %>%
#   combn(m = 2) %>%
#   data.frame() %>%
#   map_dfr(function(pair) {
#     id_1 <- pair[1]
#     id_2 <- pair[2]
#     response_1 <- filter(rating, participant_id == id_1)$response
#     response_2 <- filter(rating, participant_id == id_2)$response
#     tibble(
#       item_id = keywords$item_id,
#       familiarity = keywords$familiarity,
#       filename = keywords$filename,
#       pair_id = str_c(id_1, id_2, sep = "_"),
#       participant_id_1 = id_1,
#       participant_id_2 = id_2,
#       response_1,
#       response_2,
#       cosine = compute_cosine(response_1, response_2, word2vec)
#     )
#   })

# write_csv(rating_pairwise, here(output_dir, "rating_pairwise.csv"))

# mod_pairwise <- lmer(
#   cosine ~ familiarity + (familiarity | pair_id) + (1 | filename),
#   data = rating_pairwise
# )
# (summary_pairwise <- summary(mod_pairwise))

# Rmisc::summarySEwithin(
#   data = rating_pairwise, measurevar = "cosine", withinvars = "familiarity",
#   idvar = "pair_id", na.rm = TRUE
# ) %>%
#   ggplot(aes(x = familiarity, y = cosine, color = familiarity)) +
#   geom_violin(data = rating_pairwise) +
#   coord_cartesian(ylim = c(0.0, 1.0)) +
#   geom_pointrange(aes(ymin = cosine - se, ymax = cosine + se)) +
#   theme_classic()
```

[As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
We used latent semantic analysis with a word2vec embedding (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (Supplementary Figures 1 and 2).
In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± standard error = `r filter(rating_means, fam_condition == "familiar")$emmean` ± `r filter(rating_means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_means, fam_condition == "matching")$emmean` ± `r filter(rating_means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_means, fam_condition == "nonmatching")$emmean` ± `r filter(rating_means, fam_condition == "nonmatching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "matching - nonmatching")$df)`) = `r filter(rating_contrasts, contrast == "matching - nonmatching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "matching - nonmatching")$p_value)` (linear mixed-effects model), indicating that it was difficult for participants to know or guess the correct function of the unfamiliar objects.]{color="blue"}

@@

```{r, fig1, cache=!run$figures, fig.height=12, fig.cap="(ref:fig1-caption)"}
# Create Figure 1
plot_fig1(files_dir, evokeds, config, channel_locations, models)
```

@@

```{r, fig2, cache=!run$figures, fig.height=8.6, fig.cap="(ref:fig2-caption)"}
# Create Figure 2
plot_fig2(files_dir, evokeds, config, channel_locations, models)
```

>>>>

bibliography      : "misc/references.bib"
csl               : "misc/citation_style.csl"

@@

output:
  papaja::apa6_pdf:
    latex_engine: xelatex
    pandoc_args: ["--lua-filter=misc/color_text.lua"]

@@

```{r, setup, include=FALSE}
# Load packages
library(buildmer)
library(emmeans)
library(here)
library(knitr)
library(lmerTest)
library(MASS)
library(scales)
library(papaja)
library(eegUtils)
library(cowplot)
library(parallel)
library(reticulate)
library(tidyverse)

# Load custom helper functions
walk(list.files(here("src"), full.names = TRUE), source)

# Set options
options(readr.show_col_types = FALSE)
emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
opts_chunk$set(
  fig.pos = "tp",
  fig.width = 12,
  message = FALSE,
  out.width = "100%",
  warning = FALSE
)

# Directory paths
data_dir <- here("data")
materials_dir <- here("materials")
misc_dir <- here("misc")
output_dir <- here("output")
report_dir <- here(output_dir, "qc_reports")

# Write R package references
r_refs(here(misc_dir, "r-references.bib"), append = FALSE)

# Re-run steps that take a long time?
run <- list(
  rating_lsa = FALSE,
  eeg_processing = FALSE,
  mixed_models = FALSE,
  figures = TRUE
)
```

@@

```{r, ratings}
# Load rating study data and keywords
rating_raw <- read_csv(
  here(data_dir, "rating", "rating_data.csv"),
  col_types = cols(), locale = locale(encoding = "latin1")
)
keywords <- read_csv(
  here(materials_dir, "keywords.csv"),
  col_types = cols(
    familiarity = col_factor(levels = c("familiar", "unfamiliar")),
    item_id = col_factor()
  )
)

# Compute or load latent semantic analysis (LSA) results
if (run$rating_lsa) {
  word2vec_file <- here::here(data_dir, "rating", "vectors.txt")
  word2vec <- load_word2vec(word2vec_file)
  rating <- compute_lsa(rating_raw, keywords, word2vec)
} else {
  rating <- read_csv(
    here(output_dir, "rating.csv"),
    col_types = cols(item_id = col_factor(), participant_id = col_factor())
  )
}

# Compare cosine similarities between conditions
rating_stats <- compute_rating_stats(rating)

# Compute average cosine similarity for each item
cosines <- compute_average_cosines(rating)
```

[As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
We used latent semantic analysis with a word2vec embedding (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (Supplementary Figures 1 and 2).
In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± standard error = `r filter(rating_stats$means, fam_condition == "familiar")$emmean` ± `r filter(rating_stats$means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_stats$means, fam_condition == "matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_stats$contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_stats$means, fam_condition == "non-matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "non-matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "matching - non-matching")$df)`) = `r filter(rating_stats$contrasts, contrast == "matching - non-matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "matching - non-matching")$p_value)` (linear mixed-effects model), indicating that it was difficult for participants to know or guess the correct function of the unfamiliar objects.]{color="blue"}

@@

```{r, fig1, cache=!run$figures, fig.height=12, fig.cap="(ref:fig1-caption)"}
# Create Figure 1
plot_fig1(misc_dir, evokeds, config, channel_locations, models)
```

@@

```{r, fig2, cache=!run$figures, fig.height=8.6, fig.cap="(ref:fig2-caption)"}
# Create Figure 2
plot_fig2(misc_dir, evokeds, config, channel_locations, models)
```
